Think deep for reef resilience

### 2025-08-14 paper/paper_draft.qmd
Update methods with information on source-to-sink ratio calculation
and format doc

Reefs in each timeseries cluster were compared to identify characteristics that differ
between low, medium and high coral cover clusters. These characteristics include reef median
depth, mean timeseries DHW, mean timeseries DHW – tolerance level, Pearson’s correlation
between total coral cover and inversed DHW timeseries, proportion of coral habitable area
occupied by corals in the first timestep, ratio of source-to-sink larval connectivity and
total strength of larval connections between reefs. To analyse the DHW - tolerance levels of
reefs, heritable DHW – tolerance values were tracked over timeseries in a timestep \* taxa
\* reef \* scenario matrix. The mean timeseries DHW - tolerance was calculated over the
first four scenarios for each GCM (four from 4096 scenarios per GCM) due to computational
restraints, and then used to calculate an overall mean DHW – tolerance value for each reef
under each GCM.

>>>>

Reefs in each timeseries cluster were compared to identify characteristics that differ
between low, medium and high coral cover clusters. These characteristics include reef median
depth, mean timeseries DHW, mean timeseries DHW – tolerance level, Pearson’s correlation
between total coral cover and inversed DHW timeseries, proportion of coral habitable area
occupied by corals in the first timestep, ratio of source-to-sink larval connectivity and
total strength of all larval connections between reefs. To analyse the DHW - tolerance
levels of reefs, heritable DHW – tolerance values were tracked over timeseries in a timestep
\* taxa \* reef \* scenario matrix. The mean timeseries DHW - tolerance was calculated over
the first four scenarios for each GCM (four from 4096 scenarios per GCM) due to
computational restraints, and then used to calculate an overall mean DHW – tolerance value
for each reef under each GCM.

The ratio of source-to-sink connectivity for a target reef is calculated using @eq-so-to-si,
and represents the strength of the reef's outgoing larval flow relative to it's incoming
larval flow. Incoming connections in this calculation, do not directly represent the larval
supply gained as the population from which connections are coming from is not represented. A
source-to-sink ratio greater than 1 (a value greater than 0 on a log scale) indicates a reef
has greater outgoing than incoming larval flow.

$$
O:I = \frac{\frac{S_O}{N_O}}{\frac{S_I}{N_I}}
$$ {#eq-so-to-si}

Where:

-   $S$ denotes the total strength of connections.

-   $N$ denotes the number of connections.

-   $O$ denotes outgoing (source) connections from the target reef.

-   $I$ denotes incoming (sink) connections to the target reef.
